### 2013-12-23 MSteenhagen-CV.tex
Updated CV

\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon\\Projected submission: Autumn 2014

@@

% \ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
% 
% \ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.

@@

\ind 2009--Present. Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis. \href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Department of  Philosophy} \vspace{0.01in}}

@@

>>>>

\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon\\Projected submission: Autumn 2015

@@

\ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)

\ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.

@@

\ind 2009--2013. Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis. \href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Department of  Philosophy} \vspace{0.01in}}

@@

\ind Member of the Oxford-Sydney Research Group on Empathy and Sympathy.
